Topic and tone of political news articles in German online media.

### 2018-03-29 paper/writing/structure.tex
finish that writing
add more description

\section{Introduction}

Pluralism is an essential principle of democratic societies. An important pillar of this principle is an opinion-forming process that incorporates as many different perspectives as possible. For the process of forming opinions, information conveyed by the media, in particular the mass media of journalism, plays a decisive role. They create the preconditions for making the social and cultural diversity of modern societies visible and manageable. Securing the diversity of opinion-forming processes and preventing concentration processes in the media sector is an essential prerequisite for a functioning democracy.

Media outlets (TV, Radio, Newspaper) usually operate in two-sided markets, where they serve two customer groups (content consumer and advertiser) that are connected via indirect network effects. The new developments in digital media provide new opportunities and challenges for media outlets. The costs of providing and disseminating information have been reduced and the speed of information exchange has increased enormously. At first glance, these developments seem to have a positive effect on the provision of information. However, it also means that the incentive for media to produce primary information declines since the Internet has reduced the marginal utility of content. A study of French news websites from 2013 shows that only 38 percent of the online articles contained original content, with the remainder being copies of those originals \citep{cage_information_2017}. At the same time, the number of people who find out about current news on the Internet is increasing. According to a study on the media coverage of the German-speaking population, nearly 40\% of respondents used the internet at least once a week in 2017 to inform themselves about the current news compared to 34\% in 2016 \citep{vuma_arbeitsgemeinschaft_verbrauchs-_und_medienanalyse_verbrauchs-_2017}. Recognizing the importance of media pluralism, the European Commission has endorsed several initiatives to discuss and promote media diversity in the European Union\footnote{https://ec.europa.eu/digital-single-market/en/policies/media-freedom-and-pluralism}.

A resulting question is whether the political reporting of different content providers distinguishes itself and whether this reporting has an influence on the opinion-forming process of the voters. The aim of this paper is to investigate these questions with the use of up-to-date text mining methods. For this purpose, German online news articles about domestic politics are analyze to examine the media pluralism in the market for German-language online news. German federal elections took place on 24th of September 2017 and the formation of the government has taken up a period of about five month. The articles considered here dated from 01.06.2017 to 01.03.2018 and thus inform their readers both about the election promises of the parties (before the election) and about the coalition talks (after the election). They therefore make an important contribution to the public's opinion-forming process. The empirical strategy follows a novel approach combining "the two Ts": Topic and Tone \citep{hansen_shocking_2016}. That is, first the topics covered in the articles are identified, to find out how these topics are discussed (tone). The final step is to check whether the tonality of reporting is reflected in the survey results on voting preferences calculating the cross-correlation coefficients. More precisely, the research strategy is as follows:

@@

@@

The remaining course of the paper is as follows: In Section \ref{ch_onlinenews} the characteristics of the market for online news in Germany are outlined. \ref{ch_elections} give a brief overview about political trends in Germany in recent month. The data used to conduct the model is described in Section \ref{ch_data}. Section \ref{ch_model} explains the generative process of the structural topic model as well as the selected parameters to run the model. The empirical analysis containing the above mentioned steps is conducted in Section \ref{ch_empirical}.

@@

After the election, the formation of a government was difficult due to the large number of parties elected to the Bundestag and the considerable loss of votes by the major parties CDU/CSU and SPD. Since all parties rejected a merger with the AfD, numerically only two coalitions with an absolute parliamentary majority were possible: a grand coalition ("GroKo") of CDU/CSU and SPD, and a Jamaica coalition (coalition of CDU/CSU, FDP (economic liberal party) and B90/Die Grünen (Bündnis 90/Die Grünen, green party). The grand coalition was initially rejected by the SPD. The four-week exploratory talks on the possible formation of a Jamaica coalition officially failed on 19 November 2017 after the FDP announced its withdrawal from the negotiations. FDP party leader Christian Lindner said that there had been no trust between the parties during the negotiations. The main points of contention were climate and refugee policy. CDU and CSU regretted this result, while B90/Die Grünen sharply criticized the withdrawal of the Liberals. The then Green leader Cem Özdemir accused the FDP of lacking the will to reach an agreement.

@@

% ----------------------
% the online news market
% ----------------------
\section{The online news market}\label{ch_onlinenews}

The market for media content in Germany is characterized by the coexistence of public and private broadcasters. By shifting media content to the Internet, the dual system, which has been shaping the German television and radio landscape since the introduction of private broadcasting in the early 1980s, is facing a radical change. Since 2000, public broadcasting has expanded its range of services, particularly in the digital media sector. In 2017, 22 own websites and 100 apps were operated by public broadcasters on which they offer their content. As a result, public broadcasting no longer only competes with private television and radio stations, but also enters the market for online news. In the following, the characteristics of the market for online news in Germany are briefly described.

Private media outlets naturally appear as two-sided platforms, that allow interaction between two categories of consumers: audiences and advertisers. As the demand on both consumer-sides are linked via indirect network externalities, the market in which media outlets operate are referred to as two-sided or multi-sided markets. The theoretical literature on two-sided markets originates from the analysis of credit card markets \citep{rochet_platform_2003} and was later transferred to the concept of other industries, such as dating agencies, real estate agents, and internet “business-to-business” websites \citep{caillaud_chicken_2003}. The basic concept of two-sided markets was already discussed decades ago in several economic studies, especially on media markets \citep{corden_maximisation_1952}, \citep{gustafsson_circulation_1978}, \citep{blair_pricing_1993}. However, comprehensive analyses have only been carried out in the last ten years, starting with the works of \citet{rochet_platform_2003}, \citet{evans_empirical_2003} and \citet{armstrong_competition_2006}.

Advertising-supported media such as online newspapers are typical examples of two-sided markets where the newspaper can be conceived as platforms that allow interaction between audiences ("eyeballs") and advertisers. The newspaper creates (or buys) content to attract viewers which in turn attract advertisers who pay for readers' attention \citep{evans_industrial_2005}. The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM). Advertising can also have an effect on the recipients, which can be either negative or positive, depending on the quality of the advertising. Based on the strength of the indirect network effects, private publishers maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}. Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to obtain access to the viewers. Many online news agencies provide part of their editorial content for free and hide another, more exclusive part behind a paywall. However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only be efficient if the content behind the paywall is very exclusive. As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many eyeballs as possible to their platform, and thus, exploit the indirect network effects on the advertising site. In fact, most advertising-financed online magazines earn a large part of their gross margin from advertising \citep{evans_industrial_2005}. In order to maximize their profits, these companies have an interest in attracting as many readers as possible. In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site.

The two-sided market structure of the private news market results in news platforms striving to choose their content in such a way that its reach is as large as possible in order to maximize profits from advertising revenues. \citet{steiner_program_1952} concluded, that profit-maximizing media owners may choose to offer the same content, i.e. content aligned with the tastes of the majority. \citet{gabszewicz_press_2001} study the problem of diversity of the political content of newspapers. They find that the maximum differentiation only prevails if the readers sufficiently value the political differentiation between the newspapers the advertising market is small enough. On the other hand, advertising may also have a positive impact on the media, as it enables publishers to report independently of political parties. \citet{ellman_what_2009} analyze a theoretical framework of a two-sided market for newspaper, where readers value accuracy and advertisers value advert-receptive readers. They found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage. However, in the monopolistic case, newspapers under-report news that sufficiently reduces advertiser profits.

Given the crucial role of the media in shaping opinion and promoting democracy, pluralism of opinion and accuracy of information is a major concern of public authorities. Public broadcasting in Germany originated in the post-war period and has always had the task of providing the entire population with independent media. This media offer is intended to guarantee diversity of opinion within the media landscape and to be economically and politically independent. The former is given by the fact that the public media are financed by compulsory fees. To take into account the distinct nature of digital media, the Interstate Broadcasting Agreement (Rundfunkstaatsvertrag) also regulates the scope for action of online services offered by public service broadcasting since 2007. Accordingly, public media are not allowed to distribute purchased content and must - depending on the category of content - set a time limit on its accessibility. In addition, there is a strict advertising ban and prohibition of regional reporting.

% -----
% Data
% -----
\section{Dataset and data preparation}\label{ch_data}

Figure \ref{fig_reach} shows the largest providers of online news in terms of daily pageviews.\footnote{The figure shows the estimated percentage of daily pageviews on the internet that occurred on a specific website.} It is striking that SPIEGEL ONLINE has the greatest reach over the entire course of time followed by Bild.de. Public websites like Deutschlandfunk.de or Tagesschau.de have a rather small share in that market.

\begin{figure}[H]
	\caption{Percentage of daily pageviews}
	\includegraphics[width=\textwidth]{../figs/reach.png}
	\label{fig_reach}
\end{figure}

I conduct the estimation on a sample of 14,937 online news articles from seven news provider about domestic politics\footnote{Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, stern.de, ZEIT ONLINE, Tagesschau.de}, of which only Tagesschau.de belongs to the group of public provider. The reason for this is that the content structure of Tagesschau.de is most similar to that of the private providers. ZDF.de offers predominantly video content and DLF website mainly offers audio content in the form of interviews, which makes it hard to include it in the model. The articles are dated from 01.06.2017 to 01.03.2018. I first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started. The scraping code was written in Python and can be made available on request.} Then all articles from the section "domestic policy" are filtered by checking the URL structure.

Figure \ref{fig_distr1} shows the distribution of the number of articles from the respective news sources by date. There is a high peak around the federal elections on September, 24th.

@@

% ------------------
% Text Pre-Procesing
% ------------------
A central task in text mining is to extract low-dimensional information from documents that are high-dimensional by nature \citep{bholat_text_2015}. This is related to the task of reducing the number of unique language elements in order to reduce the dimensionality of data (to avoid unnecessary computational complexity and overfitting) while at the same time keeping those words that reflect the content of a document. Any useful representation of text will throw away some information, the trick is to include the relevant information for our needs, and exclude the extraneous information. A common strategy to use text as data and reduce the dimensionality, is to pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) to reduce the number of language elements \citep{gentzkow_text_2017}. Intuitively the term frequency (tf) of a word is a measure of how important that word may be. There are words in a document, however, that occur many times but may not be important like articles, conjunctions, and so on. These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected. We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized list of stop-words that are redundant superfluous or distorting. We also remove punctuation character (e.g. ., ,, !, ?, etc.) and all numbers from our corpus. After completing this steps we were left with 68.576 unique terms in our vocabulary.

@@

% ----------------------
% Structural topic Model
% ----------------------
\section{The structural topic model}\label{ch_model}

@@

STM has been applied to multiple academic fields: \citet{roberts_structural_2014} uses STM to analyse open-ended responses from surveys and experiments, \citet{farrell_corporate_2016} applies the model to scientific texts on climate change, revealing links between corporate funding and the framing of scientific studies. \citet{mishler_using_2015} show that "STM can be used to detect significant events such as the downing of Malaysia Air Flight 17" when applied to twitter data. Another study shows how STM can be used to explore the main international development topics of countries’ annual statements in the UN General Debate and examine the country-specific drivers of international development rhetoric \citep{baturo_what_2017}. \citet{mueller_reading_2016} use newspaper text to predict armed conflicts in different regions. They use the estimated topic shares in linear fixed effects regression to forecast conflict out-of-sample. \citet{roberts_navigating_2016} use STM to examine the role of partisanship in topical coverage using a corpus of 13,246 posts that were written for 6 political blogs during the course of the 2008 U.S. presidential election. With the aim of revealing the effect of partisan membership on topic prevalence, each blog is assigned to be either liberal or conservative. To explore the differences between the two, they look at the expected proportion of topic and examine the posts most associated with a respective topic. This approach is similar to \citet{roberts_model_2016}. They also use different measures of distance between the topic-word distributions of the same topic within different models.

@@

This process revealed that a model with 50 topics best reflects the structure in the corpus. Furthermore, the media outlet of the article is used as covariates in the topic prevalence and topical content. In other words, the corresponding newswire of an article influences the probability distribution of topics and how the topics are discussed. To address problems due to non-convexity, we rely on the spectral initialization approach advocated by \citet{roberts_navigating_2016}.

% ----------------------
% Model Results
% ----------------------
\section{Empirical Evaluation}\label{ch_empirical}

@@

We will select the following topics from the whole set (topics are ordered regarding their overall corpus frequency). The most frequent words of these topics can be seen in the appendix \ref{fig_plotquote}:

@@

Next, the differences of topic prevalence for given document characteristics can be estimated \citep{roberts_model_2016}. More specifically, I estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents (see equation \ref{eq_1}). The stm-package provides a function that uses the method of composition to incorporate uncertainty in the dependent variable, drawing a set of topic proportions from the variational posterior repeated times and compute the coefficients as the average over all results \citep{roberts_stm:_2016}.

@@

Such lexical or “bag-of-words” approaches are widely presented in the finance literature to  determine  the  effect  of  central  banks’  monetary  policy  communications on asset prices and real variables (\citet{nyman_news_2018} \citep{tetlock_giving_2007}, \citep{tetlock_more_2008}). \citet{hansen_shocking_2016} use a similar approach to measure "the two Ts" (Topic and tone). They explore the effects of FOMC statements on both market and real economic variables. To understand the multi-dimensional information a statement is transmitting, they apply LDA on a corpus of 142 FOMC decision statements split into sentences (topic). They then measure how the central bank is talking about that topic, using a dictionary approach (tone). To calculate their score, they subtract the negative words from the positive words und divide this by the number of total words of the statement. A similar score is used by \citet{nyman_news_2018}, who measure the effect of narratives and sentiment of financial market text-based data on developments in the financial system. They count the number of occurrences of excitement words and anxiety words and then scale these numbers by the total text size as measured by the number of characters.

@@

\begin{figure}[H]
	\caption{Cross-Correlation at lag 0}
	\begin{center}
			\includegraphics[width=\textwidth,keepaspectratio]{../figs/ccf.png}
			\label{fig_ccf}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\includegraphics[width=.49\textwidth]{../figs/plotquote1.png}
	\caption{}
\end{figure}

\begin{figure}[H]
	\includegraphics[width=.49\textwidth]{../figs/plotquote2.png}
	\caption{}
\end{figure}
	% 4
\begin{figure}[H]
	\includegraphics[width=.49\textwidth]{../figs/plotquote4.png}
	\caption{}
\end{figure}

	% 10
\begin{figure}[H]
	\includegraphics[width=.49\textwidth]{../figs/plotquote10.png}
	\caption{}
\end{figure}

	% 13
\begin{figure}[H]
	\includegraphics[width=.49\textwidth]{../figs/plotquote13.png}
	\caption{}
\end{figure}
	% 17
\begin{figure}[H]
	\includegraphics[width=.49\textwidth]{../figs/plotquote17.png}
	\caption{}
\end{figure}

	% 20
\begin{figure}[H]
	\includegraphics[width=.49\textwidth]{../figs/plotquote20.png}
	\caption{}
\end{figure}
	% 23
\begin{figure}[H]
	\includegraphics[width=.49\textwidth]{../figs/plotquote23.png}
	\caption{}
\end{figure}
	% 26
\begin{figure}[H]
	\includegraphics[width=.49\textwidth]{../figs/plotquote26.png}
	\caption{}
\end{figure}
	% 27
\begin{figure}[H]
	\includegraphics[width=.49\textwidth]{../figs/plotquote27.png}
	\caption{}
\end{figure}
	% 30
\begin{figure}[H]
	\includegraphics[width=.49\textwidth]{../figs/plotquote30.png}
	\caption{}
\end{figure}
	% 32
\begin{figure}[H]
	\includegraphics[width=.49\textwidth]{../figs/plotquote32.png}
	\caption{}
\end{figure}
	% 37
\begin{figure}[H]
	\includegraphics[width=.49\textwidth]{../figs/plotquote37.png}
	\caption{}
\end{figure}
	% 46
\begin{figure}[H]
	\includegraphics[width=.49\textwidth]{../figs/plotquote46.png}
	\caption{}
\end{figure}

>>>>

\section{Introduction}
% Noch deutlicher beschreiben, was eigentlich gemacht wird. Besser motivieren
% Paper von Ralf, Melissa, Tobias zitieren.

Pluralism is an essential principle of democratic societies. An important pillar of this principle is an opinion-forming process that incorporates the different perspectives represented in the society. For the process of forming opinions, information conveyed by the media, in particular the mass media of journalism, plays a decisive role. They create the preconditions for making the social and cultural diversity of modern societies visible and manageable. Securing the diversity of opinion-forming processes and preventing concentration processes in the media sector is an essential prerequisite for a functioning democracy. An important question is therefore whether the political reporting of different content providers distinguishes itself and whether this reporting has an influence on the opinion-forming process of the voters. The aim of this paper is to investigate these questions with the use of up-to-date text mining methods.

A number of different factors have an influence on the diversity of media content. These include the market structure for journalistic content and the digitization of the industry. Media outlets (TV, Radio, Newspaper) usually operate in two-sided markets, where they serve two customer groups (content consumer and advertiser) that are connected via indirect network effects. The two-sided market structure of the private news market results in news platforms striving to choose their content in such a way that its reach is as large as possible in order to maximize profits from advertising revenues. \citet{steiner_program_1952} concluded, that profit-maximizing media owners may choose to offer the same content, i.e. content aligned with the tastes of the majority. \citet{gabszewicz_press_2001} study the problem of diversity of the political content of newspapers. They find that the maximum differentiation only prevails if the readers sufficiently value the political differentiation between the newspapers the advertising market is small enough. On the other hand, advertising may also have a positive impact on the media, as it enables publishers to report independently of political parties. \citet{ellman_what_2009} analyze a theoretical framework of a two-sided market for newspaper, where readers value accuracy and advertisers value advert-receptive readers. They found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage. However, in the monopolistic case, newspapers under-report news that sufficiently reduces advertiser profits.

The new developments in digital media provide new opportunities and challenges for media outlets. The costs of providing and disseminating information have been reduced and the speed of information exchange has increased enormously. At first glance, these developments seem to have a positive effect on the provision of information. However, it also means that the incentive for media to produce primary information declines since the Internet has reduced the marginal utility of content. A study of French news websites from 2013 shows that only 38 percent of the online articles contained original content, with the remainder being copies of those originals \citep{cage_information_2017}. At the same time, the number of people who find out about current news on the Internet is increasing. According to a study on the media coverage of the German-speaking population, nearly 40\% of respondents used the internet at least once a week in 2017 to inform themselves about the current news compared to 34\% in 2016 \citep{vuma_arbeitsgemeinschaft_verbrauchs-_und_medienanalyse_verbrauchs-_2017}. Recognizing the importance of media pluralism, the European Commission has endorsed several initiatives to discuss and promote media diversity in the European Union\footnote{https://ec.europa.eu/digital-single-market/en/policies/media-freedom-and-pluralism}. One way to ensure the independence and diversity of the media landscape is through public funded media. In Germany public broadcasting originated in the post-war period and is financed by compulsory fees. To take into account the distinct nature of digital media, the Interstate Broadcasting Agreement (Rundfunkstaatsvertrag) also regulates the scope for action of online services offered by public service broadcasting since 2007. Accordingly, public media are not allowed to distribute purchased content and must - depending on the category of content - set a time limit on its accessibility. In addition, there is a strict advertising ban and prohibition of regional reporting.

With the purpose of examining the media pluralism in the market for German-language online news, this paper analyzes German online news articles about domestic politics. German federal elections took place on 24th of September 2017 and the formation of the government has taken up a period of about five month. The articles considered here dated from 01.06.2017 to 01.03.2018 and thus inform their readers both about the election promises of the parties (before the election) and about the coalition talks (after the election). They therefore make an important contribution to the public's opinion-forming process. The empirical strategy follows a novel approach combining "the two Ts": Topic and Tone \citep{hansen_shocking_2016}. That is, first the topics covered in the articles are identified, to find out how these topics are discussed (tone). The final step is to check whether the tonality of reporting is reflected in the survey results on voting preferences calculating the cross-correlation coefficients. More precisely, the research strategy is as follows:

@@

% Der erste Absatz ist z.B. ziemlich knapp. Ebenso sind „Measuring Tone“ und „Comparing with polls“ sehr knapp im Vergleich zu „Dicovering topics“ beschrieben.

@@

The remaining course of the paper is as follows: The following Section \ref{ch_elections} gives an overview about political trends in the past six month (June 2017 to March 2018). The data used to conduct the model is described in Section \ref{ch_data}. Section \ref{ch_model} explains the generative process of the structural topic model as well as the selected parameters to run the model. The empirical analysis containing the above mentioned steps is conducted in Section \ref{ch_empirical}.

@@

After the election, the formation of a government was difficult due to the large number of parties elected to the Bundestag and the considerable loss of votes by the major parties CDU/CSU and SPD. Since all parties rejected a coalition with the AfD, numerically only two coalitions with an absolute parliamentary majority were possible: a grand coalition ("GroKo") of CDU/CSU and SPD, and a Jamaica coalition (coalition of CDU/CSU, FDP (economic liberal party) and B90/Die Grünen (Bündnis 90/Die Grünen, green party)). The grand coalition was initially rejected by the SPD. The four-week exploratory talks on the possible formation of a Jamaica coalition officially failed on 19 November 2017 after the FDP announced its withdrawal from the negotiations. FDP party leader Christian Lindner said that there had been no trust between the parties during the negotiations. The main points of contention were climate and refugee policy. CDU and CSU regretted this result, while B90/Die Grünen sharply criticized the withdrawal of the Liberals. The then Green leader Cem Özdemir accused the FDP of lacking the will to reach an agreement.

@@

% -----
% Data
% -----
\section{Dataset and data preparation}\label{ch_data}
% Viel mehr Datenbeschreibung / deskriptive Statistik
% Warum wurden grade diese Medien ausgesucht?

I conduct the estimation on a sample of 14,937 online news articles from seven german news provider about domestic politics\footnote{Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, stern.de, ZEIT ONLINE, Tagesschau.de}. The articles are dated from 01.06.2017 to 01.03.2018. I first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started. The scraping code was written in Python and can be made available on request.} Then all articles from the section "domestic policy" are filtered by using the URL of an article. Figure \ref{fig_distr1} shows the distribution of the number of articles from the respective news sources by date. There is a high peak around the federal elections on September, 24th.

@@

Overall, the selected news providers are among the top ten German online news providers in the period under review, with only Tagesschau.de belonging to the public media. The reason for this is that the content structure of Tagesschau.de is most similar to that of the private providers. ZDF.de offers predominantly video content and DLF website mainly offers audio content in the form of interviews, which makes it hard to include it in the model.

% ------------------
% Text Pre-Procesing
% ------------------
% Mehr beschreiben was hier gemacht wird. Was ist z.b. eine stop-word list?

A central task in text mining is to extract low-dimensional information from documents that are high-dimensional by nature \citep{bholat_text_2015}. This is related to the task of reducing the number of unique language elements in order to reduce the dimensionality of data (to avoid unnecessary computational complexity and overfitting) while at the same time keeping those words that reflect the content of a document. Any useful representation of text will throw away some information, the trick is to include the relevant information that is needed, and exclude the extraneous information. A common strategy to use text as data and reduce the dimensionality, is to pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) to reduce the number of language elements \citep{gentzkow_text_2017}.

Intuitively the term frequency (tf) of a word is a measure of how important that word may be. There are words in a document, however, that occur many times but may not be important like articles, conjunctions, and so on. These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected. We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized list of stop-words that are redundant superfluous or distorting. We also remove punctuation character (e.g. ., ,, !, ?, etc.) and all numbers from our corpus. After completing this steps we were left with 68.576 unique terms in our vocabulary.

@@

% ----------------------
% Structural topic Model
% ----------------------
\section{The structural topic model}\label{ch_model}
% Kapitel mehr mit eigenen Worten beschreiben.

@@

STM has been applied to multiple academic fields: \citet{roberts_structural_2014} uses STM to analyze open-ended responses from surveys and experiments, \citet{farrell_corporate_2016} applies the model to scientific texts on climate change, revealing links between corporate funding and the framing of scientific studies. \citet{mishler_using_2015} show that "STM can be used to detect significant events such as the downing of Malaysia Air Flight 17" when applied to twitter data. Another study shows how STM can be used to explore the main international development topics of countries’ annual statements in the UN General Debate and examine the country-specific drivers of international development rhetoric \citep{baturo_what_2017}. \citet{mueller_reading_2016} use newspaper text to predict armed conflicts in different regions. They use the estimated topic shares in linear fixed effects regression to forecast conflict out-of-sample. \citet{roberts_navigating_2016} use STM to examine the role of partisanship in topical coverage using a corpus of 13,246 posts that were written for 6 political blogs during the course of the 2008 U.S. presidential election. With the aim of revealing the effect of partisan membership on topic prevalence, each blog is assigned to be either liberal or conservative. To explore the differences between the two, they look at the expected proportion of topic and examine the posts most associated with a respective topic. This approach is similar to \citet{roberts_model_2016}. They also use different measures of distance between the topic-word distributions of the same topic within different models.

@@

This process revealed that a model with 50 topics best reflects the structure in the corpus. Furthermore, the media outlet of the article is used as covariates in the topic prevalence and topical content. In other words, the corresponding newswire of an article influences the probability distribution of topics and how the topics are discussed.

% ----------------------
% Model Results
% ----------------------
\section{Empirical Evaluation}\label{ch_empirical}
% Besser strukturieren. Tabellen mit Ergebnissen zeigen (nicht nur Abbildungen).

@@

We will select the following topics from the whole set (topics are ordered regarding their overall corpus frequency). The most frequent words of these topics can be seen in the appendix:

@@

Next, the differences of topic prevalence for given document characteristics can be estimated \citep{roberts_model_2016}. More specifically, I estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents (see equation \ref{eq_1}). The stm-package provides a function that uses the method of composition to incorporate uncertainty in the dependent variable, drawing a set of topic proportions from the variational posterior repeated times and compute the coefficients as the average over all results \citep{roberts_stm:_2016}.
% Letzten satz umschreiben! hört sich sonst so an als würde ich nicht wissen, was die macht. 
% Formel erklären!

@@

Such lexical or “bag-of-words” approaches are widely presented in the finance literature to  determine  the  effect  of  central  banks’  monetary  policy  communications on asset prices and real variables (\citet{nyman_news_2018} \citep{tetlock_giving_2007}, \citep{tetlock_more_2008}). \citet{hansen_shocking_2016} use a similar approach to measure "the two Ts" (Topic and tone). They explore the effects of FOMC (Federal Open Market Committee) statements on both market and real economic variables. To understand the multi-dimensional information a statement is transmitting, they apply LDA on a corpus of 142 FOMC decision statements split into sentences (topic). They then measure how the central bank is talking about that topic, using a dictionary approach (tone). To calculate their score, they subtract the negative words from the positive words und divide this by the number of total words of the statement. A similar score is used by \citet{nyman_news_2018}, who measure the effect of narratives and sentiment of financial market text-based data on developments in the financial system. They count the number of occurrences of excitement words and anxiety words and then scale these numbers by the total text size as measured by the number of characters.

@@

\begin{figure}[H]
	\caption{Cross-Correlation at lag 0}
	\begin{center}
			\includegraphics[width=\textwidth,keepaspectratio]{../figs/ccf.png}
			\label{fig_ccf}
	\end{center}
\end{figure}
% Anders darstellen. 
% Eventuell auch Lags zeigen.

@@

% 1, 2
\begin{figure}[H]
	\begin{center}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote1.png}
		\end{subfigure}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote2.png}
		\end{subfigure}
	\end{center}
\end{figure}

% 4, 10
\begin{figure}[H]
	\begin{center}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote4.png}
		\end{subfigure}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote10.png}
		\end{subfigure}
	\end{center}
\end{figure}

% 13, 17
\begin{figure}[H]
	\begin{center}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote13.png}
		\end{subfigure}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote17.png}
		\end{subfigure}
	\end{center}
\end{figure}

% 20, 23
\begin{figure}[H]
	\begin{center}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote20.png}
		\end{subfigure}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote23.png}
		\end{subfigure}
	\end{center}
\end{figure}

% 26, 27
\begin{figure}[H]
	\begin{center}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote26.png}
		\end{subfigure}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote27.png}
		\end{subfigure}
	\end{center}
\end{figure}

% 30, 32
\begin{figure}[H]
	\begin{center}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote30.png}
		\end{subfigure}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote32.png}
		\end{subfigure}
	\end{center}
\end{figure}

% 37, 46
\begin{figure}[H]
	\begin{center}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote37.png}
		\end{subfigure}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote46.png}
		\end{subfigure}
	\end{center}
\end{figure}
